% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode

% Tennessee Technological University
% ENGR1120-021 - GSET - Summer 2021
% Tristan Hill - June 16, 2021
% Module 7 - Repetition
% Lecture 7 

\documentclass[fleqn]{beamer} % for presentation (has nav buttons at bottom)

\usepackage{/home/thill/Documents/lectures/cpp_workshop/modules/cpp_lectures}

\newcommand{\MNUM}{7\hspace{2mm}} % Module number
\newcommand{\TNUM}{---\hspace{2mm}} % Topic number - single topic for now
\newcommand{\moduletitle}{Repetition} % Titles and Stuff
%\newcommand{\topictitle}{---} 

\newcommand{\sectiontitleI}{Repetition and Programming} % More Titles and Stuff
\newcommand{\sectiontitleII}{Types of Loops }
\newcommand{\sectiontitleIII}{Repetition and Program Flow}
\newcommand{\sectiontitleIV}{Nested Structures}
\newcommand{\sectiontitleV}{An example in C++}

\newcommand{\btVFill}{\vskip0pt plus 1filll}

\setbeamercolor{title in head/foot}{fg=TTUgold} % this needs work...

\title{GSET - Programming with Mr. Hill}
\author{Tristan Hill\vspc \hspc Tennessee Technological University \hspc}
\date{Summer 2021}

\begin{document}

\lstset{language=MATLAB,basicstyle=\ttfamily\small,showstringspaces=false}

\frame{\titlepage \center\begin{framed}\Large \textbf{Module \MNUM - \moduletitle}\end{framed} \vspace{5mm}}


% Section 0 - Outline
\frame{
	
	\large \textbf{Module \MNUM - \moduletitle} \vspace{3mm}\\
	
	\begin{itemize}
	
		\item \hyperlink{sectionI}{\sectiontitleI} \vspc % Section I
		\item \hyperlink{sectionII}{\sectiontitleII} \vspc % Section II
		\item \hyperlink{sectionIII}{\sectiontitleIII} \vspc %Section III
		\item \hyperlink{sectionIV}{\sectiontitleIV} \vspc %Section IV	
		\item \hyperlink{sectionV}{\sectiontitleV} \vspc %Section V
	
	\end{itemize}

}


% Section I
\section{\sectiontitleI}

	% Section I - Frame I
	\begin{frame}[label=sectionI,containsverbatim] \small
		\frametitle{\sectiontitleI}
		Hove you noticed that you have repeated code in you programs? Is this OK?
		
		\begin{enumerate}
			
			\item 
			 
			\item
			
			\item
			
			\item
			
		\end{enumerate}
	
	 What can you do to reduce the length and increase the readability of your programs?
	
	\end{frame}


% Section II
\section{\sectiontitleII}

	% Section II - Frame I
	\begin{frame}[label=sectionII,containsverbatim] \small
		\frametitle{\sectiontitleII}
	
	There are different types of loops used for different situtations. 
		
	\begin{itemize}
		\item while loop (entry controlled)
		\item for loop (entry controlled)
		\item do while loop (exit controlled)	
	\end{itemize}


		
	\end{frame}


% Section III
\section{\sectiontitleIII}

	\begin{frame}[label=sectionIII,containsverbatim] \small
	\frametitle{\sectiontitleIII}
	
Previously the programs we have written look like a single line. Now, our programs began to flow in a much more complex way...  \vspace{5mm}\\
			
			\vspace{40mm}


	
	\end{frame}



% Section IV
\section{\sectiontitleIV}	
	% Section IV - Frame I
	\begin{frame}[label=sectionIV,containsverbatim] \small
		\frametitle{\sectiontitleIV}    
	
		

		 

		\btVFill
		%\tiny{ref: \href{some link}{some text}} 
	\end{frame}

		% Section IV - Frame II
	\begin{frame}[label=sectionIV,containsverbatim] \small
	\frametitle{\sectiontitleIV}    
	
	Commonly Used Flowchart Symbols
	
	\begin{itemize}
		\item Flowline
		\item Terminal
		\item Process
		\item Decision
		\item Input/Output
		\item and many more ... 
		
	\end{itemize}

	{\it Flowcharting is a tool for brainstorming and it can be used for communication and education. A flowchart is not a program. }
	
	
	\btVFill
	\tiny{ref: \href{https://en.wikipedia.org/wiki/Flowchart}{wikipedia}} 
\end{frame}

% Section V
\section{\sectiontitleV}	
	% Section V - Frame I
	\begin{frame}[label=sectionV,containsverbatim] \small
	\frametitle{\sectiontitleV}    
	

\end{frame}

		% Section V - Frame II
	\begin{frame}[label=sectionV,containsverbatim] \small
	\frametitle{\sectiontitleV}    
A simple {\bf for} loop	
	
\begin{lstlisting}

...










...			

\end{lstlisting}

	\end{frame}

		% Section V - Frame II
\begin{frame}[label=sectionV,containsverbatim] \small
\frametitle{\sectiontitleV}    

A simple {\bf while} loop	

\begin{lstlisting}

...










...			

\end{lstlisting}

\end{frame}


\end{document}

